\ttitle

### 2014-01-20 Chapters/Chapter1.tex
Remove `unknown` as environment description

To find a temporal segmentation, we rely on change detection in time series.
In the context of this research the time series consists of recordings from inertial sensors during the performance of human activities.
The sensors, such as the accelerometer, are nowadays widely available in smartphones.
We are interested in real-world data from both in- and outdoor activities in an unknown environment and in a continuous manner.

@@

\section{Scope}\label{sec:intro_scope}
The scope of this thesis are segmentation methods of inertial sensor data in the field of machine learning.
The type of data is inertial sensor time series, collected by on-body worn sensors as found in smartphones.
These time series are recorded during the performance of real-world human activities.
The setting of the activities are real-world unknown environments.

@@

Our own data set is recorded by placing a smartphone with inertial sensors in the front right pants pocket of a subject.
The subject was asked to perform common and simple activities in an uncontrolled environment, both in- and outdoors.
During the performance the subjects were also recorded with a video camera from a third-person point of view.
This allows us to create a ground truth for the temporal segmentation of performed activities.

>>>>

To find a temporal segmentation, we rely on change detection in time series.
In the context of this research the time series consists of recordings from inertial sensors during the performance of human activities.
The sensors, such as the accelerometer, are nowadays widely available in smartphones.
We are interested in real-world data from both in- and outdoor activities performed in a continuous manner.

@@

\section{Scope}\label{sec:intro_scope}
The scope of this thesis are segmentation methods of inertial sensor data in the field of machine learning.
The type of data is inertial sensor time series, collected by on-body worn sensors as found in smartphones.
These time series are recorded during the performance of real-world human activities.
The setting of the activities are real-world environments, both in- and outdoor.

@@

Our own data set is recorded by placing a smartphone with inertial sensors in the front right pants pocket of a subject.
The subject was asked to perform common and simple activities in a natural environment, both in- and outdoors.
During the performance the subjects were also recorded with a video camera from a third-person point of view.
This allows us to create a ground truth for the temporal segmentation of performed activities.

### 2014-01-20 Chapters/Chapter6.tex
Remove `unknown` as environment description

In this chapter we discuss the real-world data sets used for this research and the performance of our proposed algorithm on these data sets.
In \Cref{sec:data_sets} we discuss available data sets and argue that these are inappropriate for our research.
It is followed by an overview of the setup we have created to record our own continuous data sets in an unknown environment, both for in- and outdoor activities.
The series of activities performed are discussed in \Cref{sec:data_gathering}.
In that section we show typical plots of the inertial sensor data and stills from the video recordings.
That will illustrate the setting in which the activities are performed and the characteristics of continuous data.
The results of the algorithm are discussed in \Cref{sec:real_world_results}.
Finally, we provide a list of possible improvements in \Cref{sec:possible_improvements}.

>>>>

In this chapter we discuss the real-world data sets used for this research and the performance of our proposed algorithm on these data sets.
In \Cref{sec:data_sets} we discuss available data sets and argue that these are inappropriate for our research.
It is followed by an overview of the setup we have created to record our continuous data sets in a real-world environment, both for in- and outdoor activities.
The series of activities performed are discussed in \Cref{sec:data_gathering}.
In that section we show typical plots of the inertial sensor data and stills from the video recordings.
That will illustrate the setting in which the activities are performed and the characteristics of continuous data.
The results of the algorithm are discussed in \Cref{sec:real_world_results}.
Finally, we provide a list of possible improvements in \Cref{sec:possible_improvements}.

### 2014-01-20 Chapters/Chapter6/data_sets.tex
Remove `unknown` as environment description

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/Chapter6/data_collection/wisdm_excerpt.eps}
  \caption[WISDM Excerpt]{Excerpt from the WISDM data set \cite{kwapisz2011activity}. First five activities for subject $33$ are displayed. Due to the discontinuous nature of the recordings, this data set can not be used for change detection.}
  \label{fig:wisdm_excerpt}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/Chapter6/data_collection/uci_annotated.eps}
  \caption[UCI HAR Excerpt]{Excerpt from the UCI HAR data set \cite{anguita2012human}. The recorded training activities for subject $25$ are displayed. Due to the imprecise (and possibly incorrect) labeling and the short duration of activities, the data set can not be used for the change detection method as described in this thesis.}
  \label{fig:uci_annotated}
\end{figure}

Because of the above described shortcomings of commonly used data sets, we have decided to record activities by ourselves.
The following characterizing requirements were set for our data sets:
\begin{enumerate}
  \item The activities need to be performed and recorded in a continuous manner,
  \item The environment should be natural and uncontrolled, both in- and outdoor,
  \item The data should be clearly annotated, as objective as possible,
  \item The required hardware (and software) should be widely available.
\end{enumerate}

>>>>

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/Chapter6/data_collection/wisdm_excerpt.eps}
  \caption[WISDM Excerpt]{Excerpt from the WISDM data set \cite{kwapisz2011activity}. The first five activities of subject $33$ are displayed. Due to the discontinuous nature of the recordings, this data set can not be used for change detection.}
  \label{fig:wisdm_excerpt}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/Chapter6/data_collection/uci_annotated.eps}
  \caption[UCI HAR Excerpt]{Excerpt from the UCI HAR data set \cite{anguita2012human}. The recorded training activities of subject $25$ are displayed. Due to the imprecise (and possibly incorrect) labeling and the short duration of activities, the data set can not be used for the change detection method as described in this thesis.}
  \label{fig:uci_annotated}
\end{figure}

Because of the above described shortcomings of commonly used data sets, we have decided to record activities by ourselves.
The following requirements were set for our data sets:
\begin{enumerate}
  \item The activities need to be performed and recorded in a continuous manner,
  \item The environment should be natural and both in- and outdoor,
  \item The data should be clearly annotated, as objective as possible,
  \item The required hardware (and software) should be widely available.
\end{enumerate}
